---
title       : Demo2
subtitle    : Using GoogleVis Package for data visualization
author      : William
job         : Exchange Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : [quiz,bootstrap,shiny,interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

--- .class #id 

## Code of Chart 1

> 1. original<-read.csv("20150108.csv")
> 2. suppressPackageStartupMessages(library(googleVis))
> 3. by1<-aggregate(original$人數,by=list(original$車次,original$下車站),sum)
> 4. names(by1)<-c("Train","Station","Man")
> 5. columnOfTrainAndStation<-gvisColumnChart(by1)
> 6. plot(columnOfTrainAndStation)

```{r echo = FALSE}
original<-read.csv("20150108.csv")
suppressPackageStartupMessages(library(googleVis))
by1<-aggregate(original$人數,by=list(original$車次,original$下車站),sum)
names(by1)<-c("Train","Station","Man")
require(googleVis)
columnOfTrainAndStation<-gvisColumnChart(by1,options=list(width=1000, height=200))
plot(columnOfTrainAndStation)
```


--- .class #id

## Column Chart of Station & Train

```{r echo = FALSE,results = "asis"}
original<-read.csv("20150108.csv")
suppressPackageStartupMessages(library(googleVis))
by1<-aggregate(original$人數,by=list(original$車次,original$下車站),sum)
names(by1)<-c("Train","Station","Man")
require(googleVis)
columnOfTrainAndStation<-gvisColumnChart(by1,options=list(width=1000, height=400))
plot(columnOfTrainAndStation,tag = 'chart')
```

--- .class #id

## Column Chart of Boarding On Station Only

Boarding On Station V.S Boarding Off Station
```{r echo = FALSE,results = "asis"}
original<-read.csv("20150108.csv")
suppressPackageStartupMessages(library(googleVis))
by2<-aggregate(original$人數,by=list(original$上車站),sum)
by3<-aggregate(original$人數,by=list(original$下車站),sum)
names(by2)<-c("Station","Man")
names(by3)<-c("Station","Man")
require(googleVis)
columnOfStationOnly1<-gvisColumnChart(by2,options=list(width=1000, height=200))
columnOfStationOnly2<-gvisColumnChart(by3,options=list(width=1000, height=200))
plot(columnOfStationOnly1,tag = 'chart')
plot(columnOfStationOnly2,tag = 'chart')
```

--- .class #id

## Column Chart of Trains Only

```{r echo = FALSE,results = "asis"}
original<-read.csv("20150108.csv")
suppressPackageStartupMessages(library(googleVis))
by4<-aggregate(original$人數,by=list(original$車次),sum)
names(by4)<-c("Train","Man")
require(googleVis)
columnOfTrainOnly<-gvisBarChart(by4,options=list(width=1000, height=600))
plot(columnOfTrainOnly,tag = 'chart')
```

--- .class #id

## Order the Chart of Trains!

```{r echo = FALSE,results = "asis"}
original<-read.csv("20150108.csv")
suppressPackageStartupMessages(library(googleVis))
by4<-aggregate(original$人數,by=list(original$車次),sum)
names(by4)<-c("Train","Man")
require(googleVis)
by4<-by4[c(which(by4$Man>250)),]
by4<-by4[order(-by4[,2]),]
columnOfTrainOnly<-gvisBarChart(by4,options=list(width=1000, height=600))
plot(columnOfTrainOnly,tag = 'chart')
```

--- .class #id

## Time! -Annotated Time Line!

```{r echo = FALSE,results = "asis"}
original<-read.csv("20150108.csv")
suppressPackageStartupMessages(library(googleVis))
by5<-aggregate(original$人數,by=list(original$上車站,original$到站時間),sum)
names(by5)<-c("Station","Time","Man")
by5$Time<-strptime(by5$Time, format = "%Y%m%d %R")
require(googleVis)
columnOfTime<-gvisAnnotatedTimeLine(by5,datevar = "Time",numvar = "Man",idvar = "Station",options=list(width=1000, height=400))
plot(columnOfTime,tag =  'chart')
```

--- .class #id

## Time! -Annotated Time Chart

```{r echo = FALSE,results = "asis"}
original<-read.csv("20150108.csv")
suppressPackageStartupMessages(library(googleVis))
by5<-aggregate(original$人數,by=list(original$上車站,original$到站時間),sum)
names(by5)<-c("Station","Time","Man")
by5$Time<-strptime(by5$Time, format = "%Y%m%d %R")
require(googleVis)
columnOfTime<-gvisAnnotationChart(by5,datevar = "Time",numvar = "Man",idvar = "Station",options=list(width=1000, height=400,displayExactValues = FALSE))
plot(columnOfTime,tag =  'chart')
```

--- .class #id

## Look! -Visitor Flow Based On Station

```{r echo = FALSE,results = "asis"}
original<-read.csv("20150108.csv")
suppressPackageStartupMessages(library(googleVis))
original$到站時間<-strptime(original$到站時間, format = "%Y%m%d %R")
original$到站時間<-format(original$到站時間,'%Y-%m-%d %H')
original$到站時間<-as.factor(original$到站時間)
by6<-aggregate(original$人數,by=list(original$上車站,original$到站時間),sum)
names(by6)<-c("Station","Time","Man")
by6$Time<-strptime(by6$Time, format = "%Y-%m-%d %H")
require(googleVis)
columnOfTime<-gvisAnnotationChart(by6,datevar = "Time",numvar = "Man",idvar = "Station",options=list(width=1000, height=400,displayExactValues = TRUE))
plot(columnOfTime,tag =  'chart')
```

--- .class #id 

## Visitor Flow Based On Train

```{r echo = FALSE,results = "asis"}
original<-read.csv("20150108.csv")
suppressPackageStartupMessages(library(googleVis))
original$到站時間<-strptime(original$到站時間, format = "%Y%m%d %R")
original$到站時間<-format(original$到站時間,'%Y-%m-%d %H')
original$到站時間<-as.factor(original$到站時間)
by7<-aggregate(original$人數,by=list(original$車次,original$到站時間),sum)
names(by7)<-c("Train","Time","Man")
by7$Time<-strptime(by7$Time, format = "%Y-%m-%d %H")
require(googleVis)
columnOfTime<-gvisAnnotationChart(by7,datevar = "Time",numvar = "Man",idvar = "Train",options=list(width=1000, height=400,displayExactValues = TRUE))
plot(columnOfTime,tag =  'chart')
```
